---
title: "Study-2"
author: "Usman Afzali"
date: "2023-03-11"
format: html
---

Read the file and calculate descriptives

```{r}
scores <- read.csv("histos.csv")
psych::describe(scores)
```

Create three bins, `Lo YBOCS`, `Middle Scorers`, and `Hi YBOCS`. So, we create a new variables (YBOCS bins) to correspond with that.

```{r}
scores$YBOCSbins = ifelse(scores$YBOCS < 9, "Lo YBOCS (n = 81)", ifelse(scores$YBOCS < 20, "Middle Scorers (n = 214)", "Hi YBOCS (n = 72)"))
```

Now, make a histogram using ggplot2, and assign a different colour to each bin.

```{r}
library(ggplot2)
```

```{r}
plt1 <- ggplot(scores, aes(YBOCS, fill = YBOCSbins)) + geom_histogram(binwidth = 1) + 
  scale_fill_manual(values = c("Lo YBOCS (n = 81)" = "#249EA0",
                               "Middle Scorers (n = 214)" = "grey",
                               "Hi YBOCS (n = 72)" = "#FE980B"))
plt1
```

The same applies to the PCL-C scale below. Note the bin sizes are different here.

```{r}
scores$PCLCbins = ifelse(scores$PCLC < 28, "Lo PCL-C (n = 80)", ifelse(scores$PCLC < 58, "Middle Scorers (n = 218)", "Hi PCL-C (n = 69)"))
```

And below is the histogram

```{r}
plt2 <- ggplot(scores, aes(PCLC, fill = PCLCbins)) + geom_histogram(binwidth = 2) + 
  scale_fill_manual(values = c("Lo PCL-C (n = 80)" = "#DC593A",
                               "Middle Scorers (n = 218)" = "grey",
                               "Hi PCL-C (n = 69)" = "#3279FE"))
plt2
```

```{r}
library(patchwork)
```

Save both plots on the same plate

```{r}
plt1 + plt2
ggsave("figures/trait_plots.png", width=12, height=5)
```
